### 2016-08-01 doc/publications/plos16/plos16.tex
plos16.tex CursedForest.bib

\item check out 
  \begin{itemize}
  \item D\'iaz-Uriarte, R., \& Alvarez de Andr\'es, S. (2006). Gene selection and classification of microarray data using random
    forest. BMC Bioinformatics, 7, 3. http://doi.org/10.1186/1471-2105-7-3
  \item Goldstein et al. (2011)
  \item Chen (2012)
  \item VSURF and  varSelRF
  \end{itemize}
\end{itemize}

@@

\cite{Strobl.et.al.2007} introoduce changes to the RF algorithm to fix 1) and 2). 
However the level effect will be apparent in the CF algorithm as well. \marginpar{we can fix the boosting effect}
However, there are many examples, (particularly in genomics) whre we have data sets that are
\begin{itemize}
\item very wide
\item all variables have the same number of levels (measures at different points along the genome)
\item the hypothesied functional relationship is of a form amenable to a DT.
\end{itemize}

@@

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Methods}

@@

Cursed Forest uses:
\begin{itemize}
\item an ``information gained'' criteria for splitting.
\item variabel importance is the sum of IG over all notes and all trees for that variable
\item the model of parallelism is different to the ``foreach'' method -- we need to describe it
\end{itemize}

>>>>

\item check out 
  \begin{itemize}
  \item D\'iaz-Uriarte, R., \& Alvarez de Andr\'es, S. (2006). Gene selection and classification of microarray data using random
    forest. BMC Bioinformatics, 7, 3. http://doi.org/10.1186/1471-2105-7-3
  \item Goldstein et al. (2011)
  \item Chen (2012)
  \item VSURF and  varSelRF, 
  \item ranger package
  \item  r2VIM: A new variable selection method for random forests in
    genome-wide association studies
  \item CloudForest: A Scalable and Efficient Random Forest Implementation for Biological Data
  \end{itemize}
\end{itemize}

@@

\cite{Strobl.et.al.2007} introduce changes to the RF algorithm to fix 1) and 2). 
However the level effect will be apparent in the CF algorithm as well. \marginpar{we can fix the boosting effect}
However, there are many examples, (particularly in genomics) whre we have data sets that are
\begin{itemize}
\item very wide
\item all variables have the same number of levels (measures at different points along the genome)
\item the hypothesied functional relationship is of a form amenable to a DT.
\end{itemize}

@@

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis"

\subsubsection*{variable selection}
\cite{Genuer.et.al.2010} and \cite{Diaz.and.Alvarez.2006} describe iterative schemes for doing variable selection using the
importance measure. See \cite{Chen.and.Ishwaran.2012} for a review of the area with particular reference to genomic data.
\marginpar{ \cite{Chen.and.Ishwaran.2012} cite many papers on extensions of RF to handle GWAS data. Waht do we nned to do in this area}

\section*{Methods}

@@

Cursed Forest uses:
\begin{itemize}
\item an ``information gained'' criteria for splitting.  $f_q$ be the fraction of items labeled with value $q$ where $q= 1,
  \ldots, Q$ in a set. The  entropy of the set is $H = - \sum^{m}_{i=1} f_i \log^{}_2 f_i$
The expected information gain is the change in information entropy $H$ from a prior state $T$ to a state that takes some
information $a$ as given: 
\[ IG(T,a) = H(T) - H(T|a) \]
In this case, the  the information gain is IG = Entropy(parent node) - Weighted Sum of Entropy(Children)
\item variable importance is the sum of IG over all notes and all trees for that variable
\item the model of parallelism is different to the ``foreach'' method -- we need to describe it
\end{itemize}
